Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-12-26 manuscript/main.tex
Expand on consequences for practical forecasting

\subsection*{Practical recommendations for forecasting}

The best model in the validation period got 0.96 AAs closer to the future than the naive model.
The best model in the test period got 0.66 AAs closer to the future on average.
At a historical substitution rate of 0.0043 substitutions per site per year, we anticipate an average accumulation of 2.4 AAs per season.
Indeed, the modest improvement of our best models over a naive model of no change between years highlights the inherent difficulty and potentially limited ability to make precise forecasts for such a complex, dynamical system.

>>>>

\subsection*{Forecasting framework aids practical forecasts}

By forecasting the composition of future A/H3N2 populations with biologically-informed fitness metrics, our best models consistently outperformed a naive model (Table~\ref{table_natural_model_selection}).
While this performance confirms previously demonstrated potential for long-term influenza forecasting \cite{Luksza:2014hj}, the average gain from these models over the naive model appears low at 0.96 AA per year for validation data and 0.66 AA per year for test data.
These results are consistent with the observed dynamics of A/H3N2.
First, the one-year forecast horizon is a fraction of the average coalescence time for A/H3N2 populations of about 3--8 years \cite{}.
Hence, we expect the diversity of circulating strains to persist between seasons.
Second, the average substitution rate for A/H3N2's HA is 0.0043 substititions per site per year or an average accumulation of 2.4 AAs per year.
This accumulation of substitutions contributes to the distance between annual populations observed by the naive model.
In this context, our model gains of 0.96 and 0.66 AAs per year correspond to an explanation of 40\% and 28\% of the expected additional distance between annual populations, respectively.
This modest improvement over the naive model highlights the inherent difficulty and potentially limited ability to make precise forecasts for such a complex, dynamical system with the current framework.
